---
title: "Mobility Amid COVID-19 in U.S."
output: 
  flexdashboard::flex_dashboard:
    source_code: https://github.com/sparklingjourney/COVID-Mobility-Dashboard 
    orientation: columns
    vertical_layout: fill

---

```{r setup, include=FALSE}
library(flexdashboard)

source("DataProcessing.R")
```


Dashboard
====================================================================

Column {data-width=150}
--------------------------------------------------------------------

### Date

```{r}
valueBox(value = EndDate,icon = "fa-calendar",caption = "Date", color = "orange")
```

### Total Confirmed Cases

```{r}
#df_date
cc=sum(df_date$Confirmed_Cases_Count)
valueBox(value = cc,icon = "fa-user",caption = "Total Confirmed Cases", color = "blue")
```

### Mobility

```{r}
mi=mean(df_date$Mobility_Index)
valueBox(value = mi,icon = "fa-car",caption = "Average Mobility Index", color = "green")
```

### Tips

Hover over visualizations to view data point values and the toolkit bar for further exploration.

Column {data-width=500}
--------------------------------------------------------------------

### Motion Scatter Bubble Chart

```{r}
fig
```

Column {data-width=300}
--------------------------------------------------------------------

### Confirmed Cases Map 

```{r}
fig_cc
```


### Mobility Index Map

```{r}
fig_mi
```

About
===

Row {data-width=200}
--------------------

### Purpose

This dashboard application is developed to monitor mobility and COVID-19 development in the United States.


### Date Sources

[Johns Hopkins University](https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_US.csv), [Descartes Labs](https://raw.githubusercontent.com/descarteslabs/DL-COVID-19/master/DL-us-m50_index.csv), and U.S. Census Bureau. 

Row {data-width=600}
--------------------------------------------------

### Data Processing

1. __Extract/Aggregate__ values at the state level from each raw dataset;
2. __Integrate__ raw datasets into one master dataframe _df_;
3. __Subset__ master dataframe into a new dataframe for the most current date _df_date_;
4. __Transform__ master dataframe into another new dataframe at the monthly temporal unit _df_m_avg_

### Data Visulization

- __Value Boxes__: Total confirmed cases and mobility index on the latest date displayed
- __Motion Scatter Bubble Chart__: Monthly average of total confirmed cases and mobility index by state since March 2020. Each bubble is a state colored by region and sized by population.
- __Choropleth Maps__: Total confirmed cases and mobility index by state on the latest date displayed

Row {data-width=200}
--------------------------------------------------

### Programming Language, Libraries, and Tools

R, tidyverse, lubridate, plotly, and flexdashboard

### Contact

Feedback of the dashboard is welcomed. Please email author of this application at ayan.qu9@gmail.com.


